---
title: "01_Prepare_training_pt_data"
author: "G. Perkins"
date: "2023-03-10"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Prepare training point data 

After following the sets in PEMsamplr we are ready to model the BEC variants. Two major decision points are required. 
1) What spatial scale to model at?
2) What level of BEC classification is required 

In this example we will use the default 5m spatial resolution, and map to a site series level. We will continue using the Canyon Creek example used in PEMprepr and PEMsamplr. 




```{r cars}

#remotes::install_github("bcgov/PEMprepr", build_vignettes = TRUE)
devtools::load_all("D:\\PEM_DATA\\PEMprepr")
devtools::load_all("D:\\PEM_DATA\\PEMsamplr")
devtools::load_all("D:\\PEM_DATA\\PEMmodelr")

library(PEMprepr)
library(PEMsamplr)
library(PEMmodelr)

```


1) Generate folder structure/naming folders

```{r}
# set up the folder structure and define folder names in object fid

fid <- setup_folders("CanyonCreek")
```

We will already have a set of clean and atributed data from PEM and ensure you have a MapUnitLegend.csv set up. 


```{r}
# read in Map key 
mapkey <- read.csv(file.path(fid$AOI_dir[2], "DateCreek_MapUnitLegend.csv"))

# #read in the fuzzy index
fMat <- read.csv(file.path(AOI_dir, "_MapUnitLegend", 
                                  "fuzzy_matrix.csv")) %>%
  dplyr::select(c(target, Pred, fVal)) %>% distinct ()
fMat <- data.table(fMat)

# read in training points
allpts <- st_read(file.path(fid$training_data_1030[2], "allpts.gpkg"))
st_crs(allpts) = 3005

# read in bec data 
bec <- sf::st_read(file.path(fid$shape_dir_1010[1], "bec.gpkg")) %>% sf::st_cast(., "MULTIPOLYGON") 

```

# select the 


