---
title: "05_build_map"
author: "W.H.MacKenzie"
date: "2023-03-23"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

```

```{r  libraries}
#remotes::install_github("bcgov/PEMprepr", build_vignettes = TRUE)
devtools::load_all("D:\\GitHub\\PEMprepr")
devtools::load_all("D:\\GitHub\\PEMmodelr")

library(PEMprepr)
library(PEMmodelr)
library(terra)
library(tidyterra)

fid <- setup_folders("Deception_AOI")

```


```{r cars}

model_dir <- file.path(fid$model_final[2])
bec_zones <- as.list(list.files(model_dir))

covdir <- fid$cov_dir_1020[2]
res_folder = "5m"

# select reduced variables
reduced_vars <- read.csv(file.path(fid$model_inputs0310[2],  "reduced_covariate_list.csv")) %>% pull()

# get full raster list 
rast_list <- list.files(file.path(covdir, res_folder), pattern = ".tif$", full.names = TRUE)
rast_list <- rast_list[tolower(gsub(".tif", "", basename(rast_list))) %in% (reduced_vars)]
rstack <- terra::rast(rast_list)
template <- terra::rast(rast_list[1])
# generate tiles for mapping 

tile_dir <- file.path(model_dir, "tiles")

if(!dir.exists(file.path(tile_dir))){
  dir.create(file.path(tile_dir)) 
  # make tiles (might want to make NA tile )
  ntiles <- makeTiles(template, 500, filename= file.path(tile_dir, "tile_.tif"),  na.rm=FALSE, overwrite = TRUE)
}else if(dir.exists(file.path(tile_dir))){
  ntiles <- list.files(tile_dir, full.names = T)
}


# for each bec zone
bgcs <- list.dirs(model_dir, recursive = F,full.names = FALSE)
bgcs <- gsub("tiles", '', bgcs)

```

# loop through the bgcs 

```{r}

map_bgc <- for(b in bgcs){
  
  #b = bgcs[3]
  
  mfit = list.files(file.path(model_dir, b), recursive = TRUE, pattern = "final_model.rds$", full.names = T)
  # mfit = mfiles[1]
  model <- readRDS(file.path(mfit))
  # make the output dir
  
  out_dir <- file.path(model_dir, b,"map")
  # check if out_dir exists
  if(!dir.exists(file.path(out_dir))){ dir.create(file.path(out_dir))}
  
  predict_map(model, out_dir, tile_size = 500, tile_dir, rstack, probability = FALSE)
   
} 

```

Merge the maps together 

```{r}

bec_shp <- st_read(file.path(fid$shape_dir_1010[2],"bec.gpkg"), quiet = TRUE)%>%
  dplyr::select(MAP_LABEL)
  
map_dir <-


## Generate final map by joining BGC maps together

# load bgc layer

bec_shp <- st_read(file.path(shapes_dir, "bec.gpkg"), quiet = TRUE) %>%
  mutate(BGC_LABEL = gsub(" ","",BGC_LABEL))

aoi <- st_read(file.path(shapes_dir, "AOI.gpkg"), quiet = TRUE)

# read in map and model keys
map.key  <- read.csv(file.path(AOI_dir, "_MapUnitLegend", 
                               paste0(AOI, "_MapUnitLegend.csv")), 
                     stringsAsFactor = FALSE)


#map_dir = "D:/PEM_DATA/BEC_DevExchange_Work/Deception_AOI/3_maps_analysis/models/forest/fore_mu_bgc/67"
#map_dir = "D:/PEM_DATA/BEC_DevExchange_Work/Deception_AOI/3_maps_analysis/models/forest_non_forest/for_nfor/1"
#map_dir = "D:/PEM_DATA/BEC_DevExchange_Work/Deception_AOI/3_maps_analysis/models/forest/fore_mu_bgc/93"

#map_dir = "E:/temp/PEM_DATA/BEC_DevExchange_Work/BoundaryTSA_AOI/3_maps_analysis/models/forest/fore_mu_bgc/9"

map_dir ="D:/PEM_DATA/BEC_DevExchange_Work/EagleHills_AOI/3_maps_analysis/models/forest/fore_mu_bgc/1"


#folders <- as.list(c("ESSFmc", "ESSFmcw", "SBSmc2")) 
#folders <- as.list(c("ESSFmc","SBSmc2"))
#folders <- as.list(c("ICHmk1" , "IDFdm1", "ICHxw","MSdm1","ICHdw1","ESSFmh","ICHmw5"))
folders <- as.list(c("IDFdk1","IDFxh2"))

# step 1:  set up a key for the combined map (includes all the units)
rkey <- lapply(folders, function (f){
  
  keys <- read.csv(file.path(map_dir, f, "response_names.csv")) %>%
    mutate(model  = f)
})

rkey <- do.call("rbind", rkey)
rkey <- rkey %>% dplyr::mutate(map.response = seq(1:length(x)))


# Step 2: For each bgc, filter and mask the raster map and update key if needed

combo_map <- lapply(folders, function(f){
  
  # f <- folders[[1]]
  
  rtemp <- raster(file.path(map_dir, f, "mosaic.tif"))
  
  rtemp[is.na(rtemp[])] <- 0 
  
  # filter to only predict over bgc
  bec_filter <- bec_shp %>%
    filter(BGC_LABEL == f) %>%
    dplyr::select(BGC_LABEL) 
  
  rtemp <- raster::mask(rtemp, as(bec_filter,'Spatial'))
  
  subkey <- rkey %>% dplyr::filter(model == f) %>%
    mutate(mosaic = as.numeric(rownames(.)))
  
  # check if the key matches or needs reclassification 
  if (isTRUE(unique(subkey$mosaic == subkey$map.response))) {
    
    print("matching key")
    
  } else {
    
    print("updating key")
    
    m <- subkey %>%
      mutate(to = as.numeric(X), 
             from = as.numeric(X)+1) %>%
      dplyr::select(to, from, map.response) 
    
    reclm <-  as.matrix(m, ncol=3, byrow= TRUE)
    rtemp <-  reclassify(rtemp, reclm, right = FALSE)#, include.lowest=TRUE)
    
  }
  
  rtemp <- reclassify(rtemp, cbind(-Inf, 0, NA), include.lowest=TRUE)
  rtemp
  
})

# join all the maps together

if(length(folders) == 3) {
  
  all_key <- merge(combo_map[[1]], combo_map[[2]], overlap=TRUE)
  all_key <- merge(all_key, combo_map[[3]], overlap = TRUE)
  
} 

all_key <- merge(combo_map[[1]], combo_map[[2]], overlap=TRUE)
all_key <- merge(all_key, combo_map[[3]], overlap = TRUE)
all_key <- merge(all_key, combo_map[[4]], overlap = TRUE)
all_key <- merge(all_key, combo_map[[5]], overlap = TRUE)
all_key <- merge(all_key, combo_map[[6]], overlap = TRUE)
all_key <- merge(all_key, combo_map[[7]], overlap = TRUE)

# tidy key and output maps
rkey <- rkey %>% dplyr::select(x, model, map.response)

writeRaster(all_key, file.path(map_dir, "forest_combo_bgcs.tif"), overwrite = TRUE)

write.csv(rkey, file.path(map_dir, "response_combo_bcgs_key.csv"))


