---
title: "Model_report"
output: html_document
params:
  trDat: trDat
  acc_output: acc_output
  out_dir: out_dir
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, cache=FALSE,
                      warning = FALSE, message = FALSE,
                      results = 'show',
                      eval = TRUE)  ## flag eval = false for quick text edits

```


```{r setup libs, echo = FALSE}

## Load library
library(data.table)
library(rmarkdown)
library(knitr)
library(dplyr)
library(ggplot2)

trDat <- params$trDat
acc_output <- params$acc_output
out_dir <- params$out_dir

## testing lines
#trDat <- train_data
#acc_output <- baseout


```


```{r summary, echo = FALSE, include = TRUE}
trDat <- trDat %>% 
  dplyr::filter(position == "Orig")

#table(trDat[, "mapunit1"])

covs <- names(trDat)[12:length(names(trDat))]

```


This model uses the following parameters: 

* **mapunit:** 'mapunit1'
* **model covariates : ** `r covs`


## Response variable: 

The following training points and frequency of points were used in the model.

```{r summary1, echo = FALSE, include = TRUE}

# calculate summary of raw training data set
trDat_sum <- trDat %>%
  dplyr::group_by(mapunit1) %>%
  dplyr::summarise(freq = n()) %>%
  dplyr::mutate(prop = round(freq/sum(freq),3))

ggplot(trDat, aes(mapunit1)) +
  geom_bar() + 
  theme_pem()+
  theme(axis.text.x = element_text(angle = 90))+
  scale_fill_discrete_sequential(palette = "Light Grays")

trDat_slices <- trDat %>%
  group_by (slice) %>%
  dplyr::summarise(n.transect = length(unique(transect_id)),
                   n.sites = length(unique(tid))) %>% 
  pivot_longer(cols = c("n.transect", "n.sites"), names_to = "type", values_to = "number")

ggplot(trDat_slices, aes(slice, number, fill = type)) +
  geom_bar(stat = "identity", position = "dodge") + 
  theme_pem()+
  scale_fill_discrete_sequential(palette = "Light Grays")

```


## Comparison of leave-one-out model results

```{r, LOO overall accuracy with confidence intervals, echo = FALSE, eval = TRUE}

#Compare the LOO metrics to test metrics to see model fit 

acc <- acc_output %>%    
  dplyr::select(mapunit1, slice, spat_p_theta1,spat_p_theta.5, spat_p_theta0,      aspat_p_theta1,aspat_p_theta.5, aspat_p_theta0 ) %>%
  distinct() %>% 
  mutate(slice = factor(slice))

acc2 <- acc  %>%
  pivot_longer(cols = where(is.numeric), names_to = "accuracy_type", values_to = "value") %>%
  distinct() %>%
  mutate(type = case_when(
    accuracy_type %in% c("MLaccuracy", "OOB_inv", "kappa", "mcc") ~ "0_machine",
    stringr::str_detect(accuracy_type, "^spat_p_theta") ~ "1_spatial",
    stringr::str_detect(accuracy_type, "aspat_p_theta") ~ "2_aspatial")) %>%
  filter(!is.na(type)) %>% filter(!accuracy_type == "slice") %>%
  mutate(accuracy_type = stringr::str_replace(accuracy_type, "aspat_p_theta_", "\u0398 "),
         accuracy_type = stringr::str_replace(accuracy_type, "^spat_p_theta_", "\u0398 ")) %>%
  mutate(accuracy_type = factor(accuracy_type), type = factor(type))


overall_acc <- ggplot(aes(y = value, x = accuracy_type, fill = slice), data = acc2 ) + 
  geom_boxplot() +
  scale_fill_brewer(type = "qual") +
  facet_grid(~type, labeller = labeller(type = 
                                             c("1_spatial" = "spatial",
                                               "2_aspatial" = "aspatial")), scales = "free_x")+
  geom_hline(yintercept = 0.65,linetype ="dashed", color = "black") + 
  theme_pem_facet() +
  scale_fill_manual(values=c("grey90", "grey75", "grey50", "grey35","grey10"))+
  theme(axis.text.x = element_text(angle = 90, hjust = 1), legend.position="none") +
  xlab("Metric") + ylab("Accuracy") + 
  ylim(0, 1)

overall_acc
```


```{r, cv vs test overall accuracy with confidence intervals, echo = FALSE, eval = TRUE}

acc_sum <- acc_output %>%
    dplyr::select(slice,
        aspat_p_theta0, aspat_p_theta.5, aspat_p_theta1,
        aspat_pa_theta0, aspat_pa_theta.5, aspat_pa_theta1,
        aspat_paf_theta0, aspat_paf_theta.5, aspat_paf_theta1,
        spat_p_theta0, spat_p_theta.5, spat_p_theta1,
        spat_pa_theta0, spat_pa_theta.5, spat_pa_theta1,
        spat_paf_theta0, spat_paf_theta.5, spat_paf_theta1) %>%
  distinct()

acc_sum_long <- acc_sum %>%
     pivot_longer(cols = where(is.numeric), names_to = "accuracy_type", values_to = "value") %>%
mutate(type = case_when(
     stringr::str_detect(accuracy_type, "aspat_") ~ "aspatial",
     stringr::str_detect(accuracy_type, "spat_") ~ "spatial")) %>%
  mutate(accuracy_type_label = case_when(
    stringr::str_detect(accuracy_type, "_p_") ~ "p",
    stringr::str_detect(accuracy_type, "_pa_") ~ "pa",
    stringr::str_detect(accuracy_type, "_paf_") ~ "paf"))%>%
  mutate(valuepc = value*100)

acc_sum_long <- acc_sum_long %>%
  mutate(theta = regmatches(acc_sum_long$accuracy_type,regexpr("[0-9]+",acc_sum_long$accuracy_type))) %>%
  mutate(theta = case_when(
    theta == 5 ~ '0.5', 
    .default = theta))


# # set up order for plots 
acc_sum_long$type_f = factor(acc_sum_long$accuracy_type_label, levels = c("p" ,"pa", "paf"))

p2 <- ggplot(aes(y = valuepc, x = theta , fill = type), data = acc_sum_long ) +
   geom_boxplot() +
   facet_wrap(~accuracy_type_label, scales = "free_x", nrow = 1) +
   geom_hline(yintercept = 65,linetype ="dashed", color = "black") +
   ggtitle("Accuracy measures (median + quartiles)") +
   xlab("Metric") + ylab("Accuracy") +
   ylim(-0.05, 100)+
   theme_pem_facet()+
   scale_fill_discrete_sequential(palette = "Light Grays")

p2

```


## Accuracy per mapunit

We can compare map unit accuracy levels to assess under or acceptable performance per map units. 

```{r generate overall mapunit, echo = FALSE, eval = TRUE}
mu_acc <- acc_output %>% 
  dplyr::select(mapunit1, spat_p, spat_pa, spat_paf)

mu_long <- mu_acc %>%
     pivot_longer(cols = where(is.numeric), names_to = "accuracy_type", values_to = "value") %>%
  mutate(accuracy_label = sub(".*_", "", accuracy_type))%>%
  mutate(valuepc = value*100)


p4 <- ggplot(aes(y = valuepc, x = mapunit1, fill = accuracy_type), data = mu_long ) + 
   geom_boxplot() +
   ggtitle("Mapunit accuracy measures ") + 
   xlab("accuracy measure") + ylab("Proportion of Accurate calls") +
  # ylim(-0.05, 1)+
   theme_pem_facet()+ 
   scale_fill_discrete_sequential(palette = "Light Grays")+
  theme(axis.text.x=element_text(angle = 90, vjust = 0.5))
  
p4

